# Predicting exercise manner using activity data

The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har

The training data for this project are available here: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv


##  Libraries and Multiprocessing

```{r}
library(caret)
require(doMC)
registerDoMC(3)
```

## Load Data
```{r results="hide"}
df <- read.csv('pml-training.csv')
```

## Remove problematic columns
These columns are dates and factors; problematic for training.
```{r results="hide"}
df <- df[,-c(1:7)]
```

## Remove NearZeroVars
This takes care of all those DIV#0 values and nearZeroVar covariates.
```{r, results="hide"}
nsv <- nearZeroVar(df)
clean <- df[,-nsv]
```

## Partition Data
```{r, results="hide"}
inTrain <- createDataPartition(y=clean$classe,p=0.6,list=FALSE)
training <- clean[inTrain,]
testing <- clean[-inTrain,]
```

## Compute preProcessor
Imputing is very important because there are a ton of NAs.
```{r, results="hide"}
pre <- preProcess(training[,-94],method=c('center','scale','knnImpute','pca'))
```

## Preprocess data sets
```{r, results="hide"}
trainPC <- predict(pre,training[,-94])
testPC <- predict(pre,testing[,-94])
```

## Build model using Random Forest
This takes a long time....
```{r, results="hide"}
model <- train(training$classe ~ ., data=trainPC, method='rf')
```

## confusionMatrix against preProccessed testing set
```{r, results="show"}
confusionMatrix(testing$classe, predict(model,testPC))
```
